Tempus: Probabilistic Network Latency Verifier

### 2023-01-24 paper/5_eval.tex
[Paper] added fat tree evaluation

To appraise the performance and scalability of Tempus, we seek to answer 5 evaluation questions:
\begin{enumerate}
    \item How long does it take to run the verifier overall? How does it scale?
    \item What is the bottleneck step in the verification process?
    \item How effective is the optimization technique in reducing the verification time?
    \item How effective is the optimization technique in reducing the explored equivalence classes?
    \item How does different topologies affect optimization effectiveness?
\end{enumerate}

@@

@@

From the same result, we also note that our verifier scales gracefully over the size of the network.
The verification duration ranges from 6 seconds to around 15 minutes. 
% TODO: fat-tree scalability
To drive this point more precisely, we also evaluate the running time of fat-tree topology in various sizes.
Our results in Fig. X shows that by keeping the same type of topology and scaling them up, we increased 
our verification time almost linearly?

>>>>

To appraise the viability of our approach, we seek to answer 5 evaluation questions:
\begin{enumerate}
    \item How long does it take to run the verifier overall? How does it scale?
    \item What is the bottleneck step in the verification process?
    \item How effective is the optimization technique in reducing the verification time?
    \item How effective is the optimization technique in reducing the explored equivalence classes?
    \item How does different topologies affect optimization effectiveness?
\end{enumerate}

@@

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.5]{scalability_fattree}
    \caption{Fat Tree, red dots represent the number of convolutions}
    \label{fig:scalabilityfat}
\end{figure}

@@

From the same result, we also note that our verifier scales gracefully over the size of the network.
The verification duration ranges from 6 seconds to around 15 minutes. 
% TODO: fat-tree scalability
To drive this point more precisely, we also evaluate the running time of fat-tree topology in various sizes.
Our results in Fig. \ref{fig:scalabilityfat} shows that by keeping the same type of topology and scaling them up, we increased 
our verification time almost linearly, while the unoptimized version timed out after 2 hours.
